I would like to first thank my academic advisor, Emanuela Barberis, for guiding and supporting me through many years of research at Northeastern University and within the CMS collaboration. Ela is an exemplary physicist, and her direction of my academic research regularly challenged me to push myself as a scientist and academic.

I similarly would like to thank David Morse, who was a close collaborator on the Leptoquark analysis. His expertise on leptoquark searches, and his knowledge of our analysis framework, were indispensable in the completion of my disertation and progressing the analysis toward approval within the collaboration. Dave also oversaw the Phase-2 upgrades to the CSCs I participated in, helping me learn the ins-and-outs of the CSC system through hands-on detector work, as well as settling into the CSC group as a whole.

A special thank you to Tim Cox, the CSC DPG convener, who was a delight to work with. He took every opportunity to share his deep knowledge of the CSC conditions data with me (related to my role as contact to the AlCaDB group) and was always patient with me as I balanced my conditions-data-related workload with my physics analysis and CSC upgrade tasks. Furthermore, I would like to thank the whole CSC community, who warmly welcomed me into an exciting and unique chapter of my PhD while at CERN.

Also, a thank you to the CMS Exotica physics analysis group, for providing critical feedback on my physics analysis, ensuring that it stands up to the highest possible standards of scientific rigor.

To my fellow Northeastern/CMS collaborators and friends, Vivan, Abe, Yacine, Chad, Andrew, Tanvi, and Bingran; thank you for making my time in Boston and at CERN both a productive and enjoyable one, and for being the best travel companions on our many trips throughout Europe. And of course to my dear friends and fellow PhD candidates, Joam, Keegan, Ben, and everyone in my cohort at Northeastern, thank you for the academic support and camaraderie as we struggled through our first years of coursework and teaching, and for all the fun adventures we've had outside of academia as well; I will always cherish your friendship over these past seven years.

And last, but certainly not least, a heartfelt thank you to my family, Todd, Debbie, Natasha, Conor, and Henry. Without your support, guidance, and love, I know I would not be the man---or doctor---I am today. I love you all so much.